The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
add todo
winlen results

We observed variation in multilayer network metrics as a function of changes in social, spatial, and temporal scale.

@@

>>>>

We observed variation in multilayer network metrics as a function of changes in social, spatial, and temporal scale. 
<!-- TODO: make sure we clarify these are means of all individuals? -->

@@

Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure 6a). Individual graph strength and layer relevance increased for
all summer layers as individuals became more connected with increasing window
lengths (Figure 6c, Figure 6d). These results suggest that an increasing window
length, especially for the summer season, may be resulting in less precisely
defined seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.
